---
title: "Day5_Session1"
format: 
  html: 
    code-fold: true
    code-summary: "show me the code!"
editor: visual
execute: 
  warning: false
---

```{r}
library(tidyverse)
```

## Explore Star Wars data set

-   look at the first 6 lines of starwars

-   find the dimensions of starwars

-   make a histogram of character heights

-   make a scatterplot of height vs weight

-   stage, commit, push! Check and see changes are safely stored

```{r}
head(starwars)

dim(starwars)

ggplot(data = starwars, aes(x = height)) +
  geom_histogram()

# put dependent variable on y-axis
# having data points colored by sex
ggplot(data =starwars, aes(x = height, y = mass)) +
  geom_point(aes(color = sex))
```

## Summary Statistic Practice

-   in console run starwars\$height to show all data points in that column

-   in console run class(starwars\$height) to show type of data for height column

-   use mean() function to find means

-   use sd() function to find standard deviations

    ```{r}
    # store and calculate the mean of height column
    mean_height <- mean(starwars$height)
    # show me what mean_height is = NA; we have missing values in this vector so it will show na
    mean_height
    #lets fix it to strip na values before calculation
    mean_height <- mean(starwars$height, na.rm = TRUE)

    mean_height
    ```

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)

sd_height
```
